Report ASP20 Boost

### 2020-06-04 Reports/report_1/1_REPORT.Rmd
updated report_1

**[Why is that? kurze Erklärung]**

<!-- The concept for boosting scale parameters is the same. However, residuals for the variance estimates can not be calculated, since there is no such thing as "observed" variances for individual response values. The solution is to substitute the calculated residuals with a different term: the derivative of the loss function, which in our case is the log-likelihood of the normal distribution. Instead of estiamting stepwise residuals, one estiamtes hence stepwise the score. -->

<!-- The resulting loss fcuntion then, is defined by sum of squares oa the term: -->
<!-- ui (=deviance-residuals) - inverse predicted scores * working-residuals -->

<!-- We employed the resid-function of the asp20model class, on which our class is built on. -->
<!-- The working and response residuals are the observed values -->
<!-- minus the fitted values for the location. -->
<!-- The deviance and Pearson residuals are weighted residuals, -->
<!-- divided by the fitted values for the scale. -->

@@

**[Erklärung weiter ausführen]**

@@

* A major performance problem in our code is that small learning rates for the beta-booster cause processing time of the code to increase sharply. This remains to be solved.
*A good choice of starting values for beta and gamma may enhance performance. A possible candidate is the mean of the response.

## Further

>>>>

@@

@@

* A major performance problem in our code is that small learning rates for the beta-booster cause processing time of the code to increase sharply. This remains to be solved.
* A good choice of starting values for beta and gamma may enhance performance. A possible candidate is the mean of the response.

## Further Aspects
